This Ph.D. could not be accomplished, if I did not get supports from faculty,
family, and friends, which I would like to thank these individuals here.

The first person I need to thank is my adviser (and of course, also one of the
dissertation committee), Prof. Haryadi Gunawi. He guided me since the beginning
to the end. I have learned a lot from him from ``\textit{how to survive
Ph.D.?}'' to ``\textit{how to find a job?}''. It is my great pleasure to have him
as my adviser (and it is also a great experience to be his \textit{first}
student).

Next, I need to thank the other two committee members, Professor Shan Lu and
Professor Ravi Chugh that kindly help to be my committee. I appreciate their
time and their suggestions on my presentation (which is my job talk). I also had
a chance to work with Prof. Lu in one project which is one part in this
dissertation.  Working with Prof. Lu taught me many great lessons.

I also need to thank my colleagues (aka co-authors), Tiratat Patana-anake,
Mingzhe Hao, Pallavi Joshi, Riza Suminto, Thanh Do, Jeffrey Lukman, Huan Ke,
Cesar Stuardo, Daniar Kurniawan, and Bo Fu for their hard working; thank to
other UCARE students Shiqin Yan, Michael Tong, and Huaicheng Li to make UCARE
group lively; and thank to all my friends, department faculty and staff that
helped me many things when I was working on the dissertation.

And also I want to give big thanks to my family. The first most important one is
my mother, the woman who always supports me throughout my life, without her,
there would not be this Tanakorn. The second one is Louise, my wife; she always
helps and supports me during my hard time. The other three are my lovely
sisters, Fon, Nuch, and Nid; they always make me feel good every time I talk with
them. Lastly, I want to thank my father, a man who is my motivations for many
things including this Ph.D.

