\section{Summary of Contributions and Outline}

We summarize our contributions and present the outline for the rest of
dissertation below.

\begin{itemize}

\item \textbf{Background:} Chapter \ref{chp-bg} discusses a background of cloud
computing and cloud-scale distributed systems, and how concurrency and
scalability affect system developing.

\item \textbf{Distributed concurrency bug study and taxonomy:}: Chapter
\ref{chp-taxdc} introduces \taxdc, a DC-bug study and taxonomy. The study
provides insights how DC bugs are triggered, how they affect systems, and how
they are fixed. These insights will help future research on combating DC bugs
including model checking, bug detection, formal verification, failure diagnosis,
and failure prevention.

\item \textbf{Semantic-aware model checking:} Chapter \ref{chp-samc} presents
SAMC, a white-box approach to model check distributed systems. The approach
advances the state-of-the-art of leverageing semantic knowledges to prune out
redundant executions to tackle state space explosion. SAMC introduces some
principles of semantic awareness that can mitigate the problem and this chapter
also shows \sampro, a prototype of how SAMC approach can be adopted to
Cassandra, Hadoop, and ZooKeeper.

\item \textbf{Scalability bug study:} Chapter \ref{chp-scb} presents SCB, a
study of scalability bugs in cloud-scale distributed systems. The study
provisions foundational knowledge of how a new type of bugs happen when systems
are targeted to deploy on large scale (\eg, 500 nodes). This is the first formal
study on scalability bugs.

\item \textbf{Scalability checking methodology:} Chapter \ref{chp-sck} presents
\sck, a methodology to check scalability of systems in an economical manners.
\sck introduces an approach for developers to colocate multiple CPU-intensive
nodes on one machine to test and debug scalability bugs. With \sck, developers
can mitigate a resource contention problem and yield the similar test and debug
outcome as deploying systems on real large scale.

\item \textbf{Related work:} Chapter \ref{chp-rel} summarizes related work to
tackle build distributed system model checkers. And this chapter also gives a
brief of related research efforts to colocate multiple nodes on one machine to
test scalability of the systems.

\item \textbf{Conclusion and future work:} Chapter \ref{chp-con} concludes this
dissertation, summarizes lessons learned, and discuss research avenues to make
research work in this dissertation more complete.

\end{itemize}
