

\section{Introduction}
\XXX{4 mins}

Hi I'm Tanakorn Leesatapornwongsa. Thank you for having me today. I'm going to
talk about unearthing concurrency and scalability bugs in cloud-scale
distributed systems.

\subsection{Cloud-Scale Distributed Systems}

First, let I explain what I mean when I'm saying cloud-scale distributed
systems.

I am refering to systems that are foundation for large cloud services. The
examples of these systems are MapReduce, which is a distributed computing
framework, HDFS, a distributed file system, and Cassandra, a scalable database.

\subsection{Cloud Dependability}

These systems are wildly used in many companies. For example, Facebook has a
1000-node cluster of MapReduce. Or Apple runs 100,000 nodes of Cassandra.

If there are problems in the systems, the cloud services on top of them will be
affected. As we often see headlines about the service disruption.

% put yahoo mail outage (dec 2013), amazon ebs (apr 2011) (this outage from data
% race).
% http://twitterstatus.tumblr.com/post/99180872/tracking-down-data-inconsistencies
% Whoops - Facebook loses 1 billion photos

\subsection{What Bugs Live in The Cloud?}

These show building cloud-scale distributed systems is hard.

But why?

To answer this question, my colleagues and I studied bug reports for 6 popular
cloud systems as I show here. We looked into 21,000 bugs reported from 2011 to
2014, and filtered 3600 vital bugs to study in detail.

\subsection{What Bugs Live in The Cloud?}

From the study, we can see bugs in distributed systems are much more complex
than in single machine software.

% distributed concurrency bugs
For example, concurrency bugs in distributed systems is not only multithreading
issues, we also see concurrency bugs that come from unexpected timing of network
communication.

As simple as message X should arrive before Y, but X can arrive after Y.

And we also found new classes of bugs that are specific to distributed systems. 

Such as scalability bugs, which are bugs that don't manifest when we deploy
systems on a small cluster, but will manifest when we deploy at a large cluster.

% in slide this is a "other bugs" bullet point
Other cloud-specific bugs we see are topology and quality of service bugs.

We see that existing techniques for combating bugs in single machine software
are not sufficient.

There are many opening problems waiting for systems community to tackle. 

\subsection{Research Contributions}

And here in my research, I'm focusing on unearthing distributed concurrency and
scalability bugs.

These are my research contributions.

SAMC and TaxDC are efforts to tackle distributed concurrency bugs. 

And SCk is an effort to tackle scalability bugs.

I also had a chance to join projects related to other aspects of cloud software
such as fault tolerance and performance.

\subsection{Outline}

Here is the outline of my talk. I'll start with my effort to combat distributed
concurrency bugs.

Next, I'll talk about constructing scalability bug checking methodology.

And lastly, I'll talk about my future works and conclusion.

